We presented a streaming sensor-fault classifier that closes the detection-to-action gap of a self-supervised online anomaly detector~\citep{Wadinger2023} by attributing each flagged signal to a maintenance-relevant fault type---bias, drift, accuracy loss, or freezing---from the detector's own conditional residuals, in O(1) memory and with no history buffers. The fault taxonomy is the established one~\citep{Sharma2010,Ni2009}; the contribution is its streaming, conditional-residual realization composed directly with the detector, so that type attribution is available at the same latency and operational footprint as detection.

The headline result is practical. On real battery-depletion faults in the Intel Berkeley Lab deployment~\citep{IntelLab2004}, the composed system reaches $90\%$ real-fault detection at a $7.4\%$ healthy false-positive rate and types the detected faults predominantly as freezing ($0.93$), the correct maintenance diagnosis for a transmitter stuck at a degraded value. Online adaptation is shown to be mandatory: a static prefix model false-alarms at $0.97$ on the same diurnal stream.

Around this result we characterized the operating envelope rather than overstating it. Freezing and drift are recovered with recall $1.000$ and $0.741$ on controlled injections, while bias recall is monotone in conditional coupling---absorbed on strongly coupled signals and isolated on weakly coupled ones---so that the aggregate $0.518$ is the mean of two explained regimes. We reported two refuted claims as such: freezing is not a detection blind spot of the base detector (which catches every injected freeze, usually faster than the dedicated test, so the freeze test contributes type attribution rather than detection), and adaptation robustness arises from graded change-point suppression rather than from conditional-residual cancellation. The suppression carries a measured masking dead-band of roughly $[3\sigma, 15\sigma]$ for co-occurring faults, and the freeze test requires strict constants or per-signal calibration on steady-state signals.

We also positioned the underlying detector on a broad public benchmark: on the TSB-AD univariate split ($350$ series, $23$ domains) under strict one-pass predict-then-learn it leads on mean VUS-PR and wins the majority of series against a tuned streaming baseline and the standard floors, confirming that the layer is built on a competitive detector. The scope is correspondingly honest. The real-deployment evidence exercises principally the freezing signature, the two-signal conditional model sets a structural false-positive floor that richer instrumentation would lower, per-type ground truth is available only through injection because no public stream labels all four fault types per signal and per timestep, and the benchmark evidence is univariate---the multivariate split, where the per-row conditional-MVN cost is substantial, is left to future work. Within that scope, the system delivers a deployable typing layer that turns an adaptive detector's alarm into an actionable maintenance label, with an operating envelope that is mapped rather than assumed.
